### 2019-04-05 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Small proofreading of Chapter 4.

\paragraph{Naive policy: Random Channel Selection}

@@

\paragraph{(Unachievable) Optimal oracle policy}

@@

\paragraph{A greedy approach of the oracle strategy}

@@

\begin{figure}[!b]
    \centering
    \subfloat[10\% of dynamic devices]{\includegraphics[scale=0.5]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    \hfill
    \subfloat[30\% of dynamic devices]{\includegraphics[scale=0.5]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    \vskip\baselineskip
    \vspace*{-20pt}
    \subfloat[50\% of dynamic devices]{\includegraphics[scale=0.5]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    \hfill
    \subfloat[100\% of dynamic devices]{\includegraphics[scale=0.5]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    \caption{Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme references without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    \vspace*{-10pt}
\end{figure}

@@

Figure \ref{fig:41:from10to100} presents the evolution of the successful transmission rate, as a function of time.
The two MAB algorithms, \UCB{} and Thompson Sampling (TS), are compared against the naive random policy from below, and the two oracle policies (optimal and greedy) from above.
The results are displayed when $10\%$, $30\%$, $50\%$ and $100\%$ of the traffic is generated by dynamic devices.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[scale=0.60]{perf_learning.eps}
    \caption{Learning with \UCB{} and Thomson Sampling, with many dynamic devices. Both algorithms achieve close to optimal performance after a reasonable learning time.}
    \label{fig:41:perf_learning}
\end{figure}

@@

@@

\begin{figure}[!h]
    \centering
    \subfloat[10\% of intelligent devices]{\includegraphics[scale=0.5]{ch2_10.eps}
    \label{fig:41:ch2_10}}
    \hfill
    \subfloat[30\% of intelligent devices]{\includegraphics[scale=0.5]{ch2_30.eps}
    \label{fig:41:ch2_30}}
    \vskip\baselineskip
    \vspace*{-20pt}
    \subfloat[50\% of intelligent devices]{\includegraphics[scale=0.5]{ch2_50.eps}
    \label{fig:41:ch2_50}}
    \hfill
    \subfloat[100\% of intelligent devices]{\includegraphics[scale=0.5]{ch2_100.eps}
    \label{fig:41:ch2_100}}
    \caption{Performance of the UCB bandit algorithm for the special case of uniform repartition of the static devices, when the proportion of intelligent devices in the network increases, from $10\%$ to $100\%$ (limit scenario).}
    \label{fig:41:figure4appendix}
\end{figure}

>>>>

\paragraph{$1^{\text{st}}$ - Naive policy: Random Channel Selection}

@@

\paragraph{$2^{\text{nd}}$ - (Unachievable) Optimal oracle policy}

@@

\paragraph{$3^{\text{rd}}$ - A greedy approach of the oracle strategy}

@@

\begin{figure}[!b]
    \centering
    \subfloat[10\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{10intelligent.eps}
    \label{fig:41:10intelligent}}
    %
    \subfloat[30\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{30intelligent.eps}
    \label{fig:41:30intelligent}}
    %
    \vspace*{-10pt}
    \subfloat[50\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{50intelligent.eps}
    \label{fig:41:50intelligent}}
    %
    \subfloat[100\% of dynamic devices]{\includegraphics[width=0.52\textwidth]{100intelligent.eps}
    \label{fig:41:100intelligent}}
    % FIXME use a shorter caption for the list of figures in Appendix of the thesis: it takes lots of lines to have these (a)...(d) shown in list of figures
    \caption[Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.]{Performance of two MAB algorithms (\UCB{} and Thompson Sampling), compared to extreme reference policies without learning or oracle knowledge, when the proportion of dynamic end-devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:from10to100}
    \vspace*{-10pt}
\end{figure}

@@

Figure \ref{fig:41:from10to100} presents the evolution of the successful transmission rate, as a function of time.
The two MAB algorithms, \UCB{} and Thompson Sampling (TS), are compared against the naive random policy (which are outperformed easily by the MAB algorithms), and the two (optimal and greedy) oracle policies (which outperform slightly the MAB algorithms).
The results are displayed when $10\%$, $30\%$, $50\%$ and $100\%$ of the traffic is generated by dynamic devices.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[scale=0.65]{perf_learning.eps}
    \caption{Learning with \UCB{} and Thomson Sampling, with many dynamic devices. Both algorithms achieve close to optimal performance after a reasonable learning time.}
    \label{fig:41:perf_learning}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \subfloat[10\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_10.eps}
    \label{fig:41:ch2_10}}
    %
    \subfloat[30\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_30.eps}
    \label{fig:41:ch2_30}}
    %
    \vspace*{-10pt}
    \subfloat[50\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_50.eps}
    \label{fig:41:ch2_50}}
    %
    \subfloat[100\% of intelligent devices]{\includegraphics[width=0.47\textwidth]{ch2_100.eps}
    \label{fig:41:ch2_100}}
    \caption{Performance of the UCB bandit algorithm for the special case of uniform repartition of the static devices, when the proportion of intelligent devices in the network increases, from $10\%$ to $100\%$.}
    \label{fig:41:figure4appendix}
\end{figure}

@@

### 2019-04-05 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Small proofreading of Chapter 4.

Regarding the physical layer, we consider a QPSK constellation (\emph{Quadrature Phase-Shift Keying}). Moreover, we use simplified packets composed of two parts.
The first part is the \emph{preamble} which is used for the purpose of synchronization (phase correction).
Then, we have the \emph{index} of the user, which is a sequence of QPSK symbols.
For example, this index can be a simple QPSK symbol ($\pm1\pm1j$), or a longer sequence if the PoC have to consider more users\footnote{~With $\ell$ QPSK symbols, we can fit at most $4^{\ell}/2$ devices, and not $4^{\ell}$ due to the use of a conjugate index to send back acknowledgements from the gateway.}.
Once the gateway receives an uplink packet, it detects this index and transmits an acknowledgement which has the same frame structure, but where the index is the conjugate of the index of the uplink packet ($z \mapsto \overline{z}$, \emph{e.g.}, $1+j \mapsto 1-j$).
Thanks to this index, we can have several devices communicating with the same gateway.

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.70\linewidth]{our-demo.eps}
    \caption{Schematic of our implementation that presents the role of each USRP platform.}
    \label{fig:42:our_demo}
\end{figure}

@@

\paragraph{Video}
%
As shown below in Figure~\ref{fig:42:screenshotDemoYouTube},
we made a $6$-minute \textbf{video} to show our demonstration online, and it is available on the YouTube hosting platform, at \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.
The video shows examples of $3$ dynamic devices learning simultaneously, confirming the results of Figure~\ref{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS} for overlapping channels.
It also shows the connections between the USRP boards, the Octoclock, the master laptop etc, completing the presentation of the SCEE testbed already shown in Figure~\ref{fig:42:photosSCEETestBed}.

\begin{figure}[!h]
	\centering
    % \includegraphics[width=0.90\textwidth]{Images/screenshotDemoYouTube.png}
    \includegraphics[width=0.90\textwidth]{2-Chapters/4-Chapter/Images/screenshotDemoYouTube.png}
    \caption{Screenshot of the \textbf{video} of our demonstration, \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.}
    \label{fig:42:screenshotDemoYouTube}
\end{figure}

>>>>

Regarding the physical layer, we consider a QPSK constellation (\emph{Quadrature Phase-Shift Keying}). Moreover, we use simplified packets composed of two parts.
The first part is the \emph{preamble} which is used for the purpose of synchronization (phase correction).
Then, we have the \emph{index} of the user, which is a sequence of QPSK symbols.
For example, this index can be a simple QPSK symbol ($\pm1\pm1j$), or a longer sequence if the PoC have to consider more users.
With $\ell$ QPSK symbols, we can indeed fit at most $4^{\ell}/2 = 2^{2\ell-1}$ devices, and not $4^{\ell}$ due to the use of a conjugate index to send back acknowledgements from the gateway
Once the gateway receives an uplink packet, it detects this index and transmits an acknowledgement which has the same frame structure, but where the index is the conjugate of the index of the uplink packet ($z \mapsto \overline{z}$, \emph{e.g.}, $1+j \mapsto 1-j$).
Thanks to this index, we can have several devices communicating with the same gateway.

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.75\linewidth]{our-demo.eps}
    \caption{Schematic of our implementation that presents the role of each USRP platform.}
    \label{fig:42:our_demo}
\end{figure}

@@

\paragraph{Video}
%
As shown below in Figure~\ref{fig:42:screenshotDemoYouTube},
we realized and released a $6$-minute \textbf{video} to show our demonstration online, and it is available on the YouTube hosting platform, at \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.
The video shows examples of $3$ dynamic devices learning simultaneously, confirming the results of Figure~\ref{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS} for overlapping channels.
It also shows the connections between the USRP boards, the Octoclock, the master laptop etc, completing the presentation of the SCEE testbed already shown in Figure~\ref{fig:42:photosSCEETestBed}.

\begin{figure}[!h]
	\centering
    % \includegraphics[width=0.90\textwidth]{Images/screenshotDemoYouTube.png}
    \includegraphics[width=1.00\textwidth]{2-Chapters/4-Chapter/Images/screenshotDemoYouTube.png}
    \caption{Screenshot of the \textbf{video} of our demonstration, \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.}
    \label{fig:42:screenshotDemoYouTube}
\end{figure}

### 2019-04-05 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
Small modifications on all chapters
Small proofreading of Chapter 4.

In this section, we extend the model presented before in order to take into account the possibility for retransmission of a message after a collision.
This extension is of major importance as most protocols for real-world IoT networks can use retransmissions, and it is for instance the case of the LoRa standard.
As before, we propose and evaluate different learning strategies based on MAB algorithms.
However, the price to be paid is a shorter battery lifetime for IoT devices. So this approach would be used only for devices with strong delivery constraints (\eg, for health-care applications), or that can refuel their energy over time (\eg, for robotic applications).

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.75\linewidth]{ResultsUCB.eps}
	\caption[First comparison between the exposed heuristics for the retransmission: ``Only \UCB'', ``Random, \UCB'', ``$K$ \UCB'', and ``Delayed \UCB'']{
		Comparison between the exposed heuristics for the retransmission: \textcolor{blue}{``Only \UCB''}, \textcolor{cyan}{``Random''}, \textcolor{purple}{``\UCB''}, \textcolor{green}{``$K$ \UCB''}, and \textcolor{red}{``Delayed \UCB''}.
		The usage of the same learning policy for transmissions and retransmission is named \textcolor{blue}{``Only \UCB{}''},
		whereas the usage of a random channel selection, for both transmission and retransmission, is labeled as \textbf{``no \UCB{}''}.
		First scenario: learning helps but learning to retransmit smartly is not needed, as we observe that the \textcolor{cyan}{random retransmission} heuristic achieves similar performance than the others.
	}
	\label{fig:43:mainExperiment1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.75\linewidth]{ResultsUCB2.eps}
	\caption[First comparison between the exposed heuristics for the retransmission: Only \UCB, Random, \UCB, $K$ \UCB, and Delayed \UCB]{
		Second scenario: learning helps a lot (a gain of $30\%$ in terms of collision probability), and learning to retransmit smartly is needed.
		We observe that the \textcolor{cyan}{random retransmission} achieves poor performance compared to the others.
	}
	\label{fig:43:mainExperiment2}
\end{figure}

>>>>

In this section, we extend the model presented before, to take into account the possibility for retransmissions of a message after a collision.
This extension is of major importance: most protocols for real-world IoT networks can use retransmissions, it is for instance the case of the LoRa standard.
As before, we propose and evaluate different learning strategies based on MAB algorithms.
However, the price to be paid is a shorter battery lifetime for IoT devices. So this approach would be used only for devices with strong delivery constraints (\eg, for health-care applications), or that can refuel their energy over time (\eg, for robotic applications).

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.80\linewidth]{ResultsUCB.eps}
	\caption[First comparison between the exposed heuristics for the retransmission: ``Only \UCB'', ``Random, \UCB'', ``$K$ \UCB'', and ``Delayed \UCB'']{
		Comparison between the exposed heuristics for the retransmission: \textcolor{blue}{``Only \UCB''}, \textcolor{cyan}{``Random''}, \textcolor{purple}{``\UCB''}, \textcolor{green}{``$K$ \UCB''}, and \textcolor{red}{``Delayed \UCB''}.
		The usage of the same learning policy for transmissions and retransmission is named \textcolor{blue}{``Only \UCB{}''},
		whereas the usage of a random channel selection, for both transmission and retransmission, is labeled as \textbf{``no \UCB{}''}.
		First scenario: learning helps but learning to retransmit smartly is not needed, as we observe that the \textcolor{cyan}{random retransmission} heuristic achieves similar performance than the others.
	}
	\label{fig:43:mainExperiment1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.80\linewidth]{ResultsUCB2.eps}
	\caption[First comparison between the exposed heuristics for the retransmission: Only \UCB, Random, \UCB, $K$ \UCB, and Delayed \UCB]{
		Second scenario: learning helps a lot (a gain of $30\%$ in terms of collision probability), and learning to retransmit smartly is needed.
		We observe that the \textcolor{cyan}{random retransmission} achieves poor performance compared to the others.
	}
	\label{fig:43:mainExperiment2}
\end{figure}
